{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-26 thesis/education.tex
update HEAD commit and latest links

The PSU version of the lecture
%was given in Spring 2018, and
is available at
\url{http://www.contrib.andrew.cmu.edu/~bblum/psu-lecture.pdf}
as well as under the github link above.
Being a 70-minute lecture slot rather than 50, I extended the demo to
both find and (attempt to) verify a fix for two bugs:
one a simple data race and the other the more complicated Paradise Lost bug as above.
After finding each bug, I demonstrated using Landslide on a fixed version of the code
to show how it proves the test case correct by completing all state spaces,
or (in the case of Paradise Lost) suffers an exponentially-exploding state space.
%Not that I scientifically measured it or anything,
This extended demo seemed to help students more clearly understand Landslide's intended workflow,
at the cost of about 10-15 extra minutes of lecture time
\revisionminor{(of course, this is an anecdotal opinion, not a scientific conclusion).}

At both schools students then signed up using a Google form I emailed them,
which upon completion linked them to the Landslide user guide,
which is available at
\url{http://www.contrib.andrew.cmu.edu/~bblum/landslide-guide-p2.pdf}
(CMU version)
and at % these "at"s can optionally be adjusted to make url line breaks better
\url{http://www.contrib.andrew.cmu.edu/~bblum/landslide-guide-psu.pdf}
(PSU version)
and at
\url{https://github.com/bblum/talks/tree/master/irb}
(both versions).

>>>>

The PSU version of the lecture
was given in Spring 2018, and
is available at
\url{https://www.cs.cmu.edu/~410/landslide/psu-lecture.pdf},
as well as under the github link above.
Being a 70-minute lecture slot rather than 50, I extended the demo to
both find and (attempt to) verify a fix for two bugs:
one a simple data race and the other the more complicated Paradise Lost bug as above.
After finding each bug, I demonstrated using Landslide on a fixed version of the code
to show how it proves the test case correct by completing all state spaces,
or (in the case of Paradise Lost) suffers an exponentially-exploding state space.
%Not that I scientifically measured it or anything,
This extended demo seemed to help students more clearly understand Landslide's intended workflow,
at the cost of about 10-15 extra minutes of lecture time
\revisionminor{(of course, this is an anecdotal opinion, not a scientific conclusion).}

At both schools students then signed up using a Google form I emailed them,
which upon completion linked them to the Landslide user guide,
which is available online at
\url{https://www.cs.cmu.edu/~410/landslide/landslide-guide-p2.pdf}
(CMU version)
and at % these "at"s can optionally be adjusted to make url line breaks better
\url{https://www.cs.cmu.edu/~410/landslide/landslide-guide-psu.pdf}
(PSU version)
and at
\url{https://github.com/bblum/talks/tree/master/irb}
(both versions).

### 2018-12-26 thesis/landslide.tex
update HEAD commit and latest links

The Bochs port of Landslide is likewise open-source
\revisionminor{under the \landslidelicense license}
and available at \url{https://github.com/bblum/landslide}.
% TODO: refresh
The HEAD commit at the time of writing is 8127151.
In the event of a GitHub outage or the above link otherwise not working,
a backup of the repository
% checked out at the above commit
may be found at
% TODO: make there actually be smth at this commit
\url{https://www.cs.cmu.edu/~410/landslide.tar.bz2}.
%
The Simics port uses Simics's proprietary API and is hence unlicensed and available upon request for educational use only.
Development on the Simics port is largely frozen,
as the Bochs port implements all the same features and more,
and is also roughly 3x faster.

@@

Hence,}
the educational experiments in this thesis focus on projects which students implement
on top of provided kernel basecode which Landslide already ``understands''.
Such understanding is conferred via the annotations described in this section.
For P2 and Pintos students I supply these annotations behind the scenes,
but a CMU 15-410 student who wishes to use Landslide on her kernel project shall need to brave forth hereupon.
An alternate step-by-step guide is also available at
\url{http://www.contrib.andrew.cmu.edu/~bblum/landslide-guide-kernel.pdf}.

>>>>

The Bochs port of Landslide is likewise open-source
\revisionminor{under the \landslidelicense license}
and available at \url{https://github.com/bblum/landslide}.
The HEAD commit at the time of writing is 5e4082a.
In the event of a GitHub outage or the above link otherwise not working,
a backup of the repository
checked out at that commit
may be found at
\url{https://www.cs.cmu.edu/~410/landslide/landslide.tar.bz2}.
%
The Simics port uses Simics's proprietary API and is hence unlicensed and available upon request for educational use only.
Development on the Simics port is largely frozen,
as the Bochs port implements all the same features and more,
and is also roughly 3x faster.

@@

Hence,}
the educational experiments in this thesis focus on projects which students implement
on top of provided kernel basecode which Landslide already ``understands''.
Such understanding is conferred via the annotations described in this section.
For P2 and Pintos students I supply these annotations behind the scenes,
but a CMU 15-410 student who wishes to use Landslide on her kernel project shall need to brave forth hereupon.
An alternate step-by-step guide is also available at
\url{https://www.cs.cmu.edu/~410/landslide/landslide-guide-kernel.pdf}.

### 2018-12-26 thesis/quicksand.tex
update HEAD commit and latest links

\vspace{2em}
\qrevision{There is a fundamental disconnect between existing stateless model checkers
and human users
when it comes to testing concurrent code meaningfully within a fixed CPU budget.
Existing tools
%are configured to
test systems according to a fixed preemption strategy,
leading to runtime dependent entirely on the complexity of the test program,
which may range from minutes to tens of thousands of years.
Meanwhile, users approach testing with a finite amount of patience,
%usually in the rough order of magnitude of a day:
usually not varying from one test cycle to another as their code changes and evolves:
students frantically testing last-minute changes facing a project deadline
will likely wait no longer than an hour for test results,
while a company preparing its product for production deployment % its, not their. companies arent people :triumph:
may spend upwards of weeks on rigorous stability testing.
Regardless of the use case,
a stateless model checker committing in advance to test whichever single state space arises from its fixed strategy
is certain to either under- or over-shoot its user's needs.
A model checker which preempts the system too often will fail to complete the test in time,
and one which preempts infrequently enough to complete with time to spare will leave the user wondering if it overlooked any bugs.

@@

The contributions of this chapter were published as
{\em Stateless Model Checking with Data-Race Preemption Points}
in OOPSLA 2016 \cite{quicksand}.

>>>>

\vspace{1em}
\qrevision{There is a fundamental disconnect between existing stateless model checkers
and human users
when it comes to testing concurrent code meaningfully within a fixed CPU budget.
Existing tools
%are configured to
test systems according to a fixed preemption strategy,
leading to runtime dependent entirely on the complexity of the test program,
which may range from minutes to tens of thousands of years.
Meanwhile, users approach testing with a finite amount of patience,
%usually in the rough order of magnitude of a day:
usually not varying from one test cycle to another as their code changes and evolves:
students frantically testing last-minute changes facing a project deadline
will likely wait no longer than an hour for test results,
while a company preparing its product for production deployment % its, not their. companies arent people :triumph:
may spend upwards of weeks on rigorous stability testing.
Regardless of the use case,
a stateless model checker committing in advance to test whichever single state space arises from its fixed strategy
is certain to either under- or over-shoot its user's needs.
A model checker which preempts the system too often will fail to complete the test in time,
and one which preempts infrequently enough to complete with time to spare will leave the user wondering if it overlooked any bugs.

@@

The main contributions of this chapter were published in
the 2016 ACM SIGPLAN International Conference on Object-Oriented Programming, Systems, Languages, and Applications
(OOPSLA '16)
as
{\em Stateless Model Checking with Data-Race Preemption Points}~\cite{quicksand}.
